Decentralized Data Marketplace to Enable Trusted Machine Economy $^{\dagger}$

### 2019-12-18 paper.tex
Modify session key exchange

Next, session key $k$ should be exchanged between the data provider and consumers as shown in Figure \ref{fig:key_exchange}. The data provider can obtain public keys of each consumer from the registration contract. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the product contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to obtain the session key $k$ and signature $Sign(k)$.

@@

To create a Product Contract, the broker publishes the address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, the channel root and endpoint of MAM channel, and expected number of streaming data.

@@

Before a data provider asks a broker to certify a session key, he blinds the session key first. The blinded session key is published to the smart contract by calling $addBlindedKey()$. Also the broker should use $addSignedBlindedKey()$ to publish the signature. As a result, the key certification process is recorded on the smart contract which is traceable afterward. By the way, it is hard for an attacker to compute the session key with blinding messages and signatures on smart contracts.

The data provider encrypts the session key and broker's signature with the consumer's public key and call $addEncryptKey()$ to publish the ciphertext to the smart contract. Consumers listen to $newEncryptKey$ event and decrypt the ciphertext to obtain the session key.

>>>>

Next, session key $k$ should be exchanged between the data provider and consumers. Instead of using off-chain solution which is efficient and low-cost, we use smart contract to transfer the session key\cite{3tierDataMarket} that is easy to trace the record and prevent malicious participants to cheat others.

The trading process is shown in Figure \ref{fig:key_exchange}. The data provider can obtain public keys of each consumer from the registration contract. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the product contract by calling $addEncryptKey()$ \ref{lst:key_exchange}. Consumers listen to the $newEncryptKey$ event which is triggered when the ciphertext is updated, and decrypt the ciphertext to obtain the session key $k$ and signature $Sign(k)$.

@@

To create a Product Contract\ref{lst:constructor}, the broker publishes the address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, the channel root and endpoint of MAM channel, and expected number of streaming data.

@@

Before a data provider asks a broker to certify a session key, he blinds the session key first. The blinded session key is published to the smart contract by calling $addBlindedKey()$\ref{lst:key_certification}. Also the broker should use $addSignedBlindedKey()$\ref{lst:key_certification} to publish the signature. As a result, the key certification process is recorded on the smart contract which is traceable afterward. By the way, it is hard for an attacker to compute the session key with blinding messages and signatures on smart contracts.
